---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  comment = "#>"
)
```
# covid-19-indicators
Epidemiological Indicators of COVID-19. If you would like to add information, have ideas or found a mistake, send a PR or open an issue.


## [Case Fatality Rate](https://en.wikipedia.org/wiki/Case_fatality_rate)

```{r,message=FALSE}
suppressPackageStartupMessages(library(dplyr))
cfr_data <- readr::read_csv("data/COVID-19-Indicators - CFR.csv")
from_percent <- function(x) {
  as.numeric(gsub("%", "", x, fixed = TRUE)) / 100
}
cfr_data <- mutate(cfr_data, 
  Estimate = from_percent(Estimate),
  UI_Lower = from_percent(UI_Lower),
  UI_Upper = from_percent(UI_Upper)
)

```

```{r}
library(scales)
suppressPackageStartupMessages(library(glue))
cfr_data %>% 
  arrange(desc(Published)) %>%
  transmute(
    `Point Estimate` = percent(Estimate, accuracy = 0.01),
    `Uncertainty Interval` = glue("({percent(1 - UI_alpha)} {UI_Type}: {percent(UI_Lower)}-{percent(UI_Upper)})"),
    N = N,
    Place = Place,
    Time = Time,
    `Age Group` = Age_Group,
    Published = Published,
    Reference = glue("[{Reference}]({Reference_Url})")
  ) %>% 
  knitr::kable()
```

## [Incubation Period](https://en.wikipedia.org/wiki/Incubation_period)


| Estimate in Days | Type | Uncertainty Interval           | N | Place/Time | Published | Reference |
| -------------: |-------------|-------------| -----:|-----|-----|-----|
| 5.1   | Median  | (95% CI: 4.5-5.8) | 181 | Persons with confirmed SARS-CoV-2 infection outside Hubei province, China. | 2020-03-10 | [(Lauer et al., 2020), Ann Intern Med.](https://www.ncbi.nlm.nih.gov/pubmed/32150748) |
| 11.5     | 97.5% quantile | (95% CI: 8.2-15.6) | 181 | Persons with confirmed SARS-CoV-2 infection outside Hubei province, China. | 2020-03-10 | [(Lauer et al., 2020), Ann Intern Med.](https://www.ncbi.nlm.nih.gov/pubmed/32150748) |
| 5.0    | Mean | (95% CrI: 4.2-6.0) | 52 | China?, excluding Wuhan residents | 2020-02-17 | [(Linton et al., 2020), J. Clin. Med..](https://www.mdpi.com/2077-0383/9/2/538) |
| 5.6    | Mean | (95% CrI: 5.0-6.3) | 158 | China?, including Wuhan residents | 2020-02-17 | [(Linton et al., 2020), J. Clin. Med..](https://www.mdpi.com/2077-0383/9/2/538) |
| 5.2  | Mean | (95% CI: 4.1-7.0) | 425 | Wuhan, Hubei Province, China, in December 2019 and January 2020 | 2020-01-29 | [(Qun et al., 2020), NEJM](https://www.nejm.org/doi/full/10.1056/NEJMoa2001316) |
| 12.5  | 95% quantile | (95% CI: 4.1-7.0) | 425 | Wuhan, Hubei Province, China, in December 2019 and January 2020 | 2020-01-29 | [(Qun et al., 2020), NEJM](https://www.nejm.org/doi/full/10.1056/NEJMoa2001316) |





## [Serial Interval](https://en.wikipedia.org/wiki/Serial_interval)

* "[...] 12.6% of the serial intervals in our sample were negative." [Ref](https://doi.org/10.3201/eid2606.200357). Models need to account for negative serial intervals.

| Estimate in Days | Type | Uncertainty Interval           | N  | Place/Time | Published | Reference |
| -------------: |-------------|-------------| -----:|-----|-----|-----|
| 3.96    | Mean  | (95% CI: 3.53-4.39) | 468  | Mainland China outside of Hubei Province during January 21–February 8, 2020 | 2020-03-19 | [(Du et al., 2020), Emerging Infectious Diseases](https://doi.org/10.3201/eid2606.200357) |
| 4.75    | SD  | (95% CI: 4.46-5.07) | 468  | Mainland China outside of Hubei Province during January 21–February 8, 2020 | 2020-03-19 | [(Du et al., 2020), Emerging Infectious Diseases](https://doi.org/10.3201/eid2606.200357) |
| 4.6    | Median  | (95% CrI: 3.5-5.9) | 18  | ? | 2020-03-02 | [(Nishiura et al., 2020), Int J Infect Dis.](https://www.ncbi.nlm.nih.gov/pubmed/32145466) |
| 4.4      | Mean | (95% CI: 2.9−6.7) | 21  | Hong Kong from January 16 to February 15, 2020 | 2020-02-25 | [(Zhao et al., 2020), medrxiv](https://www.medrxiv.org/content/10.1101/2020.02.21.20026559v1.article-info) |
| 7.5   | Mean | (95% CI: 5.3-19) | 425 | Wuhan, Hubei Province, China, in December 2019 and January 2020 | 2020-01-29 | [(Qun et al., 2020), NEJM](https://www.nejm.org/doi/full/10.1056/NEJMoa2001316) |

## WHO Publication Database

The WHO maintains a database of all COVID-19 related studies. This is a good starting point if you want to contribute instead of text searches on pubmed (what I did in the beginning).

* https://www.who.int/emergencies/diseases/novel-coronavirus-2019/global-research-on-novel-coronavirus-2019-ncov
